Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-05 WSSSPE1_report/WSSSPE1_summary_report.tex
work in cross-cutting section

\item From discussion in Phil Bourne's keynote:
\begin{itemize}
\item Can sustainability be defined as the effort that happens to make
  the essential things continue?
\item What is sustainability? What is it that we want to sustain? Is
  what we want to sustain valuable? Who cares if it goes away and how
  do you measure how much they care?
\end{itemize}

\item from discussion in developing panel

@@

\item from discussion in policy panel

>>>>

The question of what was meant by ``sustainability'' in the context of software
came up in many different parts of the workshop, specifically in one of the
keynotes, the Developing and Maintaining Software panel, and the Policy panel. \todo{check closing discussion notes for this topic}

In his keynote, Phil Bourne suggested that perhaps sustainability can be defined
as the effort that happens to make the essential things continue. This leads to
having to decide what it is that we want to sustain, if what we want to sustain is
valuable, and finally, who would care if it went away, and how does one measure
how much they care.

\note{rest of section will be turned from bullets into text...}

In the Developing and Maintaining Software panel,

@@

In the Policy panel,
